hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-06-24 inst/manuscript/paper.Rmd
copy edit and rerender

---
title: ""
output: word_document
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
bibliography: ms_refs.bib
csl: apa.csl
---

@@

**hatchR** is fully open source and reproducible. Source code and data can be found at <https://github.com/bmait101/hatchR/>. The Rmardkdown document with all the code to reproduce the examples from this manuscript is available at <https://github.com/bmait101/hatchR/blob/master/inst/manuscript/paper.Rmd>. The The latest version will be archived upon acceptance of the manuscript.

@@

**Box 5.** Output of `plot_phenolgy()` function using predicted hatch time from `woody_island` dataset.

>>>>

---
title: ""
output: pdf_document
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
bibliography: ms_refs.bib
csl: apa.csl
---

@@

**hatchR** is fully open source and reproducible. Source code and data can be found at <https://github.com/bmait101/hatchR/>. The Rmardkdown document with all the code to reproduce the examples from this manuscript is available at <https://github.com/bmait101/hatchR/blob/master/inst/manuscript/paper.Rmd>. The latest version will be archived upon acceptance of the manuscript.

@@

**Box 5.** Output of `plot_phenology()` function using predicted hatch time from `woody_island` dataset.
